\vspace{5em}On Evaluating Adversarial Robustness

### 2019-02-21 paper.tex
Add version number to paper
Make date auto-update

@@

\vspace{20em}
Please direct correspondence to the GitHub repository \\
\url{https://github.com/evaluating-adversarial-robustness/adv-eval-paper} \\
\noindent \\
Last Update: 18 February, 2019. \\ %TODO CHANGE OTHER DATE TOO
\newpage

@@

This checklist is a living document that lists the most common evaluation
flaws as of 18 February, 2019. We expect the evaluation flaws that are % TODO change other date too
common today will \emph{not} be the most common flaws in the future.
%
We intend to keep this checklist up-to-date with the latest recommendations
for evaluating defenses by periodically updating its contents.
Readers should check the following URL  for the most recent
revision of the checklist:
\url{https://github.com/evaluating-adversarial-robustness/adv-eval-paper}.

>>>>

\input{version}
\pdfinfo{
    /Revision (\version)
}

@@

\vspace{20em}
Please direct correspondence to the GitHub repository \\
\url{https://github.com/evaluating-adversarial-robustness/adv-eval-paper} \\
\noindent \\
Last Update: \today\ (revision \texttt{\version}).
\newpage

@@

This checklist is a living document that lists the most common evaluation
flaws as of \today. We expect the evaluation flaws that are
common today will \emph{not} be the most common flaws in the future.
%
We intend to keep this checklist up-to-date with the latest recommendations
for evaluating defenses by periodically updating its contents.
Readers should check the following URL  for the most recent
revision of the checklist:
\url{https://github.com/evaluating-adversarial-robustness/adv-eval-paper}.
